\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[thinlines]{easytable}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{bbm}
\usepackage{textcomp}
\usepackage{relsize}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{color}
\usepackage{mathtools}
\usepackage{multicol}
\setcounter{MaxMatrixCols}{20}
\allowdisplaybreaks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MATLAB code listing
%
% This is the color used for MATLAB comments below
\definecolor{MyDarkGreen}{rgb}{0.0,0.4,0.0}
 
% For faster processing, load Matlab syntax for listings
\lstloadlanguages{Matlab}%
\lstset{language=Matlab, % Use MATLAB
frame=single, % Single frame around code
basicstyle=\tiny\ttfamily, % Use small true type font
keywordstyle=[1]\color{Blue}\bfseries, % MATLAB functions bold and blue
keywordstyle=[2]\color{Purple}, % MATLAB function arguments purple
keywordstyle=[3]\color{Blue}\underbar, % User functions underlined and blue
identifierstyle=, % Nothing special about identifiers
% Comments small dark green courier
commentstyle=\usefont{T1}{pcr}{m}{sl}\color{MyDarkGreen}\tiny,
stringstyle=\color{Purple}, % Strings are purple
showstringspaces=false, % Don't put marks in string spaces
tabsize=5, % 5 spaces per tab
%
%%% Put standard MATLAB functions not included in the default
%%% language here
morekeywords={xlim,ylim,var,alpha,factorial,poissrnd,normpdf,normcdf},
%
%%% Put MATLAB function parameters here
morekeywords=[2]{on, off, interp},
%
%%% Put user defined functions here
morekeywords=[3]{FindESS, homework_example},
%
morecomment=[l][\color{Blue}]{...}, % Line continuation (...) like blue comment
numbers=left, % Line numbers on left
firstnumber=1, % Line numbers start with line 1
numberstyle=\tiny\color{Blue}, % Line numbers are blue
stepnumber=5 % Line numbers go in steps of 5
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\newcommand\scalemath[2]{\scalebox{#1}{\mbox{\ensuremath{\displaystyle #2}}}}
% \scalemath{1.0}


%opening
\title{Efficient Computation of the Dynamic Model for Krang}
\author{Munzir Zafar}

\begin{document}

\maketitle

In our earlier report we derived the model of the robot, Golem Krang, using Kane's formulation. Since the purpose of deriving the model
is either simulation or control, both of which require us to calculate the dynamics of the robot as fast as possible, we are stuck with a problem.
Due to large number of degrees of freedom, the final expression for the dynamics of the system is extremely long. Also, it contains a repetition
of same combination of terms. Thus the computation using the final form that will come out as a result of applying the results of the report
mentioned earlier, are going to be inefficient. Even if the final expression is not directly used but the resursive formulation is used to 
calculate the terms still suffers with the same problem. For this reason, it will be nice if we can reduce the amount of computation time
that is required to compute the dynamics of the system in run-time.

We use the ideas presented in \cite{kane1983use}. The basic idea is simple. As we derive the kinematics of the system recursively, we keep substituting the resulting expressions,
that are combinations of more than one variables, with one new variable. And we derive the kinematics of the succeeding links (in the serial structure) in terms 
of the substitute variables. And then we repeat this substitution process at each step. This allows us to express the final expression in simpler closed forms,
and alse if the substitutions are encoded, a potential recurring combination of variables will be evaluated/computed just once within an iteration thus
resulting the overall computation time significantly.




\tiny
\input{../../2-matlab/EfficientKanes/dynamicModelAuto2.tex}

\bibliographystyle{plain}
\bibliography{reference}

\end{document}
